Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-05 paper/JMNotes.Rmd
mention s2 spherical geometries

>>>>

>>It is planned to provide a more consistent interface that supports all CRS and allows the use of distance measures in projected planar space or using great circle distances on the unprojected ellipsoid, in the case of unprojected CRS.

- In case, you didn't know: from 1.0.0 onwards, sf uses s2 by default, i.e. spherical geometries.
Hence, I am not sure if there is really much more work to do (see https://r-spatial.github.io/sf/articles/sf7.html).
